New lower bounds for Schur and weak Schur numbers

### 2022-02-24 article/soumission_SIAM/schur.tex
dossier siam

\begin{theorem}
\label{thm:Stemp}
	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there is an S-template with width \(q\) and \(n+1\) colors 
	and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets then there is a partition of \([\![1,pq+m_{n+1}
	-1]\!]\) into \(n+k\) sum-free subsets. Number \(m_{n+1}\) denotes the minimum element colored with the special color in the \(S\)-template.
\end{theorem}

@@

A S-template with \(n\) colors is said to be symmetric if the partition into \(n\) sum-free subsets derived 
from this template by applying the extension procedure of theorem \ref{thm:Stemp} with a sum-free partition of length 1 is symmetric. 
\end{definition}

@@

\par
Inequalities (\ref{S(n+1)}), (\ref{S(n+2)}), and (\ref{S(n+3)}) cannot be further improved (with this definition of S-template). 
Inequality (\ref{S(n+4)}) cannot be further improved by only searching for symmetric S-templates whose special color is the 
last in the order of apparition (and with a multiplicative factor less than or equal to 118). Inequality (\ref{S(n+5)}) can most 
likely be further improved but the improvement probably will not be substantial. Finally, a S-template corresponding to inequality 
(\ref{S(n+6)}) was found by extending into a S-template the Schur 6-partition used in \cite{rowley2021improved} (owing to the 
size of this template, its interest is limited and since it can easily be derived from above mentioned partition, it is not given in 
\ref{S-templates}). Although we could not find a better S-template with seven colors, inequality (\ref{S(n+6)}) can definitely be 
improved by a wide margin.

>>>>

\begin{theorem}
\label{thm:Stemp}
	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there are an \(S\)-template with width \(q\) and \(n+1\) colors 
	and a sum-free \(k\)-partition of \([\![1,p]\!]\) then there is a partition of \([\![1,pq+m_{n+1}
	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{n+1}\) denotes the minimum element colored with the special color in the \(S\)-template.
\end{theorem}

@@

An S-template with \(n\) colors is said to be symmetric if the sum-free \(n\)-partition derived 
from this template by applying the extension procedure of Theorem \ref{thm:Stemp} with a sum-free 
partition with length one is symmetric. 
\end{definition}

@@

\par
Inequalities (\ref{S(n+1)}), (\ref{S(n+2)}), and (\ref{S(n+3)}) cannot be further improved (with this definition of S-template). 
Inequality (\ref{S(n+4)}) cannot be further improved by only searching for symmetric S-templates whose special color is the 
last in the order of apparition (and with a multiplicative factor less than or equal to 118). Inequality (\ref{S(n+5)}) can most 
likely be further improved but the improvement probably will not be substantial. Finally, an S-template corresponding to inequality 
(\ref{S(n+6)}) was found by extending into a S-template the Schur 6-partition used in \cite{rowley2021improved} (owing to the 
size of this template, its interest is limited and since it can easily be derived from above mentioned partition, it is not given in 
\ref{S-templates}). Although we could not find a better S-template with seven colors, inequality (\ref{S(n+6)}) can definitely be 
improved by a wide margin.
